### 2013-10-04 Tex/chapters/appendix.tex
Korrekturen von Rechtschreib- und Formulierungsfehlern

\subsection{Finite Size Effects at the Example of the Specific Heat}
\label{appendix:finiteSizeEffects}
    In Fig.\ \ref{fig:smeared_out_appendix}\subref{sfig:smeared_out_appendix:c} the specific heat
    \begin{equation}
        c = \frac{N}{T^2}\avg{\avg{E^2} - \avg{E}^2}
    \end{equation}
    is plotted for different system sizes. The finite size effects are obvious.
    The divergence is finite and gets steeper with larger \(L\). Besides
    the maximum moves to the critical temperature with larger \(L\).\\
    In Fig.\ \ref{fig:smeared_out_appendix}\subref{sfig:smeared_out_appendix:logL} the maxima of a
    cubic spline interpolation of \(c\) is plotted. Note that no errorbars
    are estimated. As mentioned before,
    this maximum increases logarithmically. One sees that a logarithmic
    fit is not worse than the power law fit. But to confirm the expected
    logarithmic growth, one would need much larger systems. Also the one
    would estimate the maximum by other means than an interpolation.
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:smeared_out_appendix:c}
            \includegraphics[width=0.45\textwidth]{plots/Specific_Heat_0}
        }
        \subfigure[][]
        {
            \label{sfig:smeared_out_appendix:logL}
            \includegraphics[width=0.45\textwidth]{plots/Specific_Heat_0_log}
        }
        \caption[Finite Size Effects by Example of the Specific Heat]
        {
            \subref{sfig:smeared_out_appendix:c} Effects of different system sizes on the specific heat \(c\)
            at \(\sigma = 0\). Dotted lines are guides to the eye.
            \subref{sfig:smeared_out_appendix:logL} maxima of \(c\) fitted
            with a power law function and a logarithm.
        }
        \label{fig:smeared_out_appendix}
    \end{figure}

>>>>

\subsection{Finite Size Effects at the Example of the Specific Heat}
\label{appendix:finiteSizeEffects}
    In Fig.\ \ref{fig:smeared_out_appendix}\subref{sfig:smeared_out_appendix:c} the specific heat
    \begin{equation}
        c = \frac{N}{T^2}\avg{\avg{E^2} - \avg{E}^2}
    \end{equation}
    is plotted for different system sizes. The finite size effects are obvious.
    The divergence is finite and gets steeper with larger \(L\). Besides
    the maximum moves to the critical temperature with larger \(L\).\\
    In Fig.\ \ref{fig:smeared_out_appendix}\subref{sfig:smeared_out_appendix:logL} the maxima of the
    cubic spline interpolation of \(c\) are plotted as a function of the
    system size \(L\). Note that no errorbars
    are estimated. As mentioned before
    this maximum increases logarithmically. One sees that a logarithmic
    fit is not worse than the power law fit. But to confirm the expected
    logarithmic growth, one would need much larger systems. Also the one
    would estimate the maximum by other means than an interpolation.
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:smeared_out_appendix:c}
            \includegraphics[width=0.45\textwidth]{plots/Specific_Heat_0}
        }
        \subfigure[][]
        {
            \label{sfig:smeared_out_appendix:logL}
            \includegraphics[width=0.45\textwidth]{plots/Specific_Heat_0_log}
        }
        \caption[Finite Size Effects by Example of the Specific Heat]
        {
            \subref{sfig:smeared_out_appendix:c} Effects of different system sizes on the specific heat \(c\)
            at \(\sigma = 0\). Dotted lines are guides to the eye.
            \subref{sfig:smeared_out_appendix:logL} Maxima of \(c\) fitted
            with a power law function and a logarithm.
        }
        \label{fig:smeared_out_appendix}
    \end{figure}

### 2013-10-04 Tex/chapters/conclusion.tex
Korrekturen von Rechtschreib- und Formulierungsfehlern

In this thesis the properties of an Ising ferromagnet, which nodes are
moved by a Gaussian distributed displacement up to the limiting case of
a Poisson process, is studied with Monte Carlo
Simulations. The neighbor relationship is provided by two proximity graphs
-- the RNG and the GG. These graphs conserve the two-dimensional, planar
character of the lattice. The coupling constants
are distance dependent, with increasing distance the coupling strength
decreases exponentially.
This model is within the universality of the square lattice Ising
ferromagnet. Its critical temperature decreases with increasing disorder
on a RNG. The reason is that the decreasing average coordination number
of the underlying graph lowers the resistance to spin flips within
strongly polarized configurations at low temperatures.
On a GG \(T_c\) first jumps, increases up to a maximum and decreases
afterwards. At high disorder it approaches the limit of randomly generated
graphs of the respective type. The course of the critical temperatures
can be made plausible observing the degree of the underlying graph, an
approximate analytic statement as reason for the observed behavior was
also presented.

\subsection{Outlook}
    The behavior of the normalized critical temperatures in dependence
    on \(\sigma\) of the Relative Neighborhood graph and Gabriel graph
    are qualitatively similar to each other. One could study the behavior
    of other proximity graphs like the minimum spanning tree or the
    Delaunay triangulation to examine if it is also similar.\\

>>>>

In this thesis the properties of an Ising ferromagnet, which nodes are
moved by a Gaussian distributed displacement up to the limiting case of
a Poisson process, is studied with Monte Carlo
Simulations. The neighbor relationship is provided by two proximity graphs
-- the RNG and the GG. These graphs conserve the two-dimensional, planar
character of the lattice. The coupling constants
are distance dependent, with increasing distance the coupling strength
decreases exponentially.
This model is within the universality of the square lattice Ising
ferromagnet. Its critical temperature decreases with increasing disorder
on a RNG.
On a GG \(T_c\) first jumps, increases up to a maximum and decreases
afterwards. At high disorder it approaches the limit of randomly generated
graphs of the respective type. The course of the critical temperatures
can be made plausible observing the degree of the underlying graph.
The decreasing average coordination number
of the underlying graph lowers the resistance to spin flips within
strongly polarized configurations at low temperatures.
An approximation of the critical temperature from the degree of the graph
an the type of the graph was given.

\subsection{Outlook}
    The curves of an \(T(K)\) plot for the RNG and GG are distinct. One
    could study the behavior of other proximity graphs like the minimum
    spanning tree or the Delaunay triangulation to examine if their critical
    temperatures would fall on other curves or lie on the curve of e.g.\ the RNG.\\
    Also the approach of investigating the Binder Cumulant as a function
    of the correlation length \(g(\xi)\), which is more
    sensitive detecting nonuniversalities\cite{Hartmann2013}, could be considered.\\
    It would also be interesting if one could find a better approximation
    of \(T_c\) considering not only the degree but also other graph
    properties like the mean edge length or edge weight.

### 2013-10-04 Tex/chapters/results.tex
Korrekturen von Rechtschreib- und Formulierungsfehlern

    agreement and of comparable precision.\\
    These values of \(T_c\) are plotted as a function of \(\sigma\) in Fig.\ \ref{fig:Tc}.

@@

@@

            \subfigure[][]
            {
                \label{sfig:Tc_norm_deg:RNG}
                \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm_deg}
            }
            \subfigure[][]
            {
                \label{sfig:Tc_norm_deg:GG}
                \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm_deg}
            }
            \subfigure[][]
            {
                \label{sfig:Tc_norm_deg_fit:RNG}
                \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm_deg_fit}
            }
            \subfigure[][]
            {
                \label{sfig:Tc_norm_deg_fit:GG}
                \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm_deg_fit}
            }

@@

                Top: Degree \(K\) of graph over different
                \subref{sfig:deg:RNG} the RNG and
                \subref{sfig:deg:GG} the GG.
                Middle: Critical temperatures normalized by degree over different
                \subref{sfig:Tc_norm_deg:RNG} the RNG and
                \subref{sfig:Tc_norm_deg:GG} the GG.
                Bottom: Critical temperatures normalized by the in Fig.\ \ref{fig:Tc_K}

@@

            \label{fig:Tc_deg}

@@

        The great influence of \(K\) on \(T_c\) is shown in Fig.\ \ref{fig:Tc_K}.
        In fact a fit of a power law function \(T_c = aK^b\) gives a reasonable
        approximation of \(T_{c}\). But large values for the \(\chi^{2}\)
        seem to indicate that this is only an approximation which does not
        account for every detail of the curve. These details will be
        investigated.\\
        In Fig.\ \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg_fit:RNG}\subref{sfig:Tc_norm_deg_fit:GG}
        the normalization is done using the power law function obtained through the fit from Fig.\ \ref{fig:Tc_K}.
        The amplitude of the curve shrinks which is a hint, that this is a good
        approximation. But it is not a constant, so there have to be other
        influences as supposed before.
        Note that even after the normalization, the values of \(T_c / K\)
        for the RNG are smaller than those for the GG.\\

@@

            \includegraphics[width=0.45\textwidth]{plots/Tc_K}
            \caption[Critical Temperature as a Function of the Degree of the Graph]
                The critical temperature is plotted as a function of the
                This is further examined in Fig.\ \ref{fig:Tc_deg}.
            \label{fig:Tc_K}

@@

            \caption[Examples of GG for different $\sigma$]
            {
                GG with periodic boundary conditions for different \(\sigma\).
                The number of edges increases from \subref{sfig:GG_sigma:0.00}
                to \subref{sfig:GG_sigma:0.01} significantly. Until \subref{sfig:GG_sigma:0.15}
                it increases and after that the number of edges decreases.
            }
            \label{fig:GG_sigma}
        \end{figure}\\
        The evolution of the RNG with increasing \(\sigma\) can be made plausible
        with the same arguments. Fig. \ref{fig:RNG_sigma}
        shows that for \(\sigma \lesssim 0.1\) the square lattice character is
        preserved -- no new edges arise and only a few existing edges vanish, which
        explains the plateau in the \(T_{c}\) diagram. With
        increasing \(\sigma\), more and more edges vanish\footnote{See also \url{http://www.youtube.com/watch?v=rltzi15mTM4} for an animation.},
        thus reducing the degree and consequently the corresponding value of \(T_{c}\).
        \begin{figure}[htb]
            \centering
            \subfigure[][$\sigma = 0.09$]
            {
                \label{sfig:RNG_sigma:0.09}
                \includegraphics[width=0.30\textwidth]{images/RNG/out009}
            }
            \subfigure[][$\sigma = 0.15$]
            {
                \label{sfig:RNG_sigma:0.15}
                \includegraphics[width=0.30\textwidth]{images/RNG/out015}
            }
            \subfigure[][$\sigma = 0.21$]
            {
                \label{sfig:RNG_sigma:0.21}
                \includegraphics[width=0.30\textwidth]{images/RNG/out021}
            }

@@

    \subsubsection{Influence of the Coupling Constant on the Critical Temperature}%
    \label{sssec:J}
        However, note that the degree does not alone influence the behavior of \(T_c\).
        Further \(T_c\) depends on the coupling constant \(J_{ij}\), which is
        obvious from Eqs.\ \eqref{eq:exactTc} and \eqref{eq:exactHCTc}. The
        coupling constant in turn is depending on the length of the edges,
        which changes with \(\sigma\).
        Therefore  in Fig.\ \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
        the mean sum of the coupling constants to all neighbors
        \begin{equation}
            \avg{\sum_{\avg{i,j}} J_{ij}}
        \end{equation}
        is plotted. This is a number which should combine the dependence on
        the degree and the coupling constant. It is determined by summing
        over the edge weights of all edges connected to a node and averaging
        this value over all nodes. Alternatively it is the average edge weight
        of all edges of the graph multiplied by the degree \(\avg{J_{ij}} K\).
        The plot Fig.\ \ref{fig:Tc_J} shows that
        there is a less obvious dependency between \(T_c\) and \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
        than between \(T_c\) and \(K\) (c.f.\ Fig.\ \ref{fig:Tc_K}).
        \begin{figure}[htbp]
            \centering
            \includegraphics[width=0.45\textwidth]{plots/Tc_J}
            \caption[Critical Temperature as a Function of the Degree of the Graph]
            {
                The critical temperature is plotted as a function of the
                average edge weight. The curve shows a less straight line
                than Fig.\ \ref{fig:Tc_K}.
            }
            \label{fig:Tc_J}
        \end{figure}\\
        Though Eq.\ \eqref{eq:exactHCTc} and Fig.\ \ref{fig:Tc_J} show
        that there is no linear connection between \(J\) and \(T_c\), the best guess
        is a linear connection, because this model is derived from the
        square lattice, where the connection is linear. Therefore, one
        normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
        Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
        jump on the GG arises again, but \(T_c\) is now monotonically
        decreasing with increasing disorder parameter \(\sigma\).
        \begin{figure}[hbtp]
            \centering
            \subfigure[][]
            {
                \label{sfig:sumJ:RNG}
                \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
            }
            \subfigure[][]
            {
                \label{sfig:sumJ:GG}
                \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
            }

@@

    \subsubsection{Course of the Critical Temperature with Fixed Coupling Constants}
    \label{appendix:fixedCoupling}
        A quick analysis of this model with fixed coupling constants \(J = 1\)
        (i.e.\ \(\alpha=0\)) is performed. The results are displayed in Fig.\ \ref{fig:Tc_deg_A0}.
        The jump from \(\sigma=0\) to \(\sigma>0\) does not disappear as in Fig.\ \ref{fig:Tc_deg}
        for variable \(J\) with \(\alpha=0.5\). This suggests that the
        disappearance of the jump is a random special case for the function
        \(J_{ij}=e^{\alpha(1-d_{ij})}\) at \(\alpha=0.5\).\\
        The simulations were carried out on \(L \in \{16,32,64\}\) lattices
        for a subset of the \(\sigma\) and \(T\) used in the previous simulation.
        Also note that the degree \(K\) is
        the same used in \ref{fig:Tc}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
        because it is obviously independent of \(J\).
        Further, note that for small values of \(\sigma\), \(T_c / K\)
        obtained using the fixed coupling strength \(J=1\) coincides with
        \(T_c / \avg{\sum_{\avg{i,j}}J_{ij}}\) obtained using the distance
        dependent coupling strength (see Eq.\ \ref{eq:coupling}).
        This can be expected from the approximate analytic statement presented
        in Sec.\ \ref{sssec:J}.
        \begin{figure}[htb]
            \centering
            \subfigure[][]
            {
                \label{sfig:Tc:RNG_A0}
                \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_A0}
            }
            \subfigure[][]
            {
                \label{sfig:Tc:GG_A0}
                \includegraphics[width=0.45\textwidth]{plots/GG_Tc_A0}
            }

>>>>

    \end{table}
    \begin{figure}[h!]

@@

    agreement and of comparable precision. These values of \(T_c\) are
    plotted as a function of \(\sigma\) in Fig.\ \ref{fig:Tc}.

@@

            \subfigure[][]
            {
                \label{sfig:Tc_norm_deg:RNG}
                \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm_deg}
            }
            \subfigure[][]
            {
                \label{sfig:Tc_norm_deg:GG}
                \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm_deg}
            }

            \caption[Critical Temperature Normalized by Degree of the Graph]
            {
                Top: Degree \(K\) of the graph over different
                disorder parameters \(\sigma\) for
                \subref{sfig:deg:RNG} the RNG and
                \subref{sfig:deg:GG} the GG.
                Bottom: Critical temperatures normalized by degree over different
                disorder parameters for
                \subref{sfig:Tc_norm_deg:RNG} the RNG and
                \subref{sfig:Tc_norm_deg:GG} the GG.
            }
            \label{fig:Tc_deg}
        \end{figure}\\
        The great influence of \(K\) on \(T_c\) becomes even more obvious
        by plotting \(T_{c}\) as a function of \(K\) as done in Fig.\ \ref{fig:Tc_deg_fit}\subref{sfig:Tc_K}.
        In fact a fit of a power law function \(T_c = aK^b\) gives a reasonable
        approximation of \(T_{c}\). But large values for the \(\chi^{2}\)
        seem to indicate that this is only an approximation which does not
        account for every detail of the curve. These details will be
        investigated.\\
        In Fig.\ \ref{fig:Tc_deg_fit}\subref{sfig:Tc_norm_deg_fit:RNG}\subref{sfig:Tc_norm_deg_fit:GG}
        the normalization is done using the power law function obtained through the fit from Fig.\ \ref{fig:Tc_deg_fit}\subref{sfig:Tc_K}.
        The amplitude of the curve shrinks which is a hint, that this is a good
        approximation. But it is not a constant, so there have to be other
        influences as supposed before.
        Note that even after the normalization, the values of \(T_c / K\)
        for the RNG are smaller than those for the GG.\\
        \begin{figure}[htbp]
            %~ \centering
            \subfigure[][]
            {
                \label{sfig:Tc_K}
                \includegraphics[width=0.45\textwidth]{plots/Tc_K}
            }

            \subfigure[][]
            {
                \label{sfig:Tc_norm_deg_fit:RNG}
                \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm_deg_fit}
            }
            \subfigure[][]
            {
                \label{sfig:Tc_norm_deg_fit:GG}
                \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm_deg_fit}
            }

@@

                \subref{sfig:Tc_K} The critical temperature is plotted as a function of the
                This is further examined in \subref{sfig:Tc_norm_deg_fit:RNG}
                and \subref{sfig:Tc_norm_deg_fit:GG} where the
                critical temperatures are normalized by the

@@

            \label{fig:Tc_deg_fit}

@@

@@

        The most promising candidate is the coupling constant \(J_{i,j}\), i.e.\ the
        distance of the nodes of the graph.
        Also the fact that the fits for the RNG and the GG yield other exponents,
        i.e.\ they are on different lines, proofs that the graph type has
        also an major influence beyond the degree.\\

@@

            \caption[Examples of GG for different $\sigma$]
            {
                GG with periodic boundary conditions for different \(\sigma\).
                The number of edges increases from \subref{sfig:GG_sigma:0.00}
                to \subref{sfig:GG_sigma:0.01} significantly. Until \subref{sfig:GG_sigma:0.15}
                it increases and after that the number of edges decreases.
            }
            \label{fig:GG_sigma}
        \end{figure}\\
        The evolution of the RNG with increasing \(\sigma\) can be made plausible
        with the same arguments. Fig.\ \ref{fig:RNG_sigma}
        shows that for \(\sigma \lesssim 0.1\) the square lattice character is
        preserved -- no new edges arise and only a few existing edges vanish, which
        explains the plateau in the \(T_{c}\) diagram. With
        increasing \(\sigma\), more and more edges vanish\footnote{See also \url{http://www.youtube.com/watch?v=rltzi15mTM4} for an animation.},
        thus reducing the degree and consequently the corresponding value of \(T_{c}\).
        \begin{figure}[htb]
            \centering
            \subfigure[][$\sigma = 0.09$]
            {
                \label{sfig:RNG_sigma:0.09}
                \includegraphics[width=0.30\textwidth]{images/RNG/out009}
            }
            \subfigure[][$\sigma = 0.15$]
            {
                \label{sfig:RNG_sigma:0.15}
                \includegraphics[width=0.30\textwidth]{images/RNG/out015}
            }
            \subfigure[][$\sigma = 0.21$]
            {
                \label{sfig:RNG_sigma:0.21}
                \includegraphics[width=0.30\textwidth]{images/RNG/out021}
            }

@@

    \subsubsection{Influence of the Coupling Constant on the Critical Temperature}%
    \label{sssec:J}
        However, note that the degree does not alone influence the behavior of \(T_c\).
        Further \(T_c\) depends on the coupling constant \(J_{ij}\), which is
        obvious from Eqs.\ \eqref{eq:exactTc} and \eqref{eq:exactHCTc}. The
        coupling constant in turn is depending on the length of the edges,
        which changes with \(\sigma\).
        Therefore  in Fig.\ \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
        the mean sum of the coupling constants to all neighbors
        \begin{equation}
            \avg{\sum_{\avg{i,j}} J_{ij}}
        \end{equation}
        is plotted. This is a number which should combine the dependence on
        the degree and the coupling constant. It is determined by summing
        over the edge weights of all edges connected to a node and averaging
        this value over all nodes. Alternatively it is the average edge weight
        of all edges of the graph multiplied by the degree \(\avg{J_{ij}} K\).
        The plot Fig.\ \ref{fig:Tc_J} shows that
        there is a less obvious dependency between \(T_c\) and \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
        than between \(T_c\) and \(K\) (c.f.\ Fig.\ \ref{fig:Tc_deg_fit}\subref{sfig:Tc_K}.).
        \begin{figure}[htbp]
            \centering
            \includegraphics[width=0.45\textwidth]{plots/Tc_J}
            \caption[Critical Temperature as a Function of the Degree of the Graph]
            {
                The critical temperature is plotted as a function of the
                average edge weight. The curve shows a less straight line
                than Fig.\ \ref{fig:Tc_deg_fit}\subref{sfig:Tc_K}..
            }
            \label{fig:Tc_J}
        \end{figure}\\
        Though Eq.\ \eqref{eq:exactHCTc} and Fig.\ \ref{fig:Tc_J} show
        that there is no linear connection between \(J\) and \(T_c\), the best guess
        is a linear connection, because this model is derived from the
        square lattice, where the connection is linear. Therefore, one
        normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
        Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
        jump on the GG arises again, but \(T_c\) is now monotonically
        decreasing with increasing disorder parameter \(\sigma\).
        \begin{figure}[hbtp]
            \centering
            \subfigure[][]
            {
                \label{sfig:sumJ:RNG}
                \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
            }
            \subfigure[][]
            {
                \label{sfig:sumJ:GG}
                \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
            }

@@

    \subsubsection{Course of the Critical Temperature with Fixed Coupling Constants}
    \label{appendix:fixedCoupling}
        A quick analysis of this model with fixed coupling constants \(J = 1\)
        (i.e.\ \(\alpha=0\)) is performed. The results are displayed in Fig.\ \ref{fig:Tc_deg_A0}.
        The jump from \(\sigma=0\) to \(\sigma>0\) does not disappear as in Fig.\ \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:GG}
        for variable \(J\) with \(\alpha=0.5\). This suggests that the
        disappearance of the jump is a random special case for the function
        \(J_{ij}=e^{\alpha(1-d_{ij})}\) at \(\alpha=0.5\).\\
        The simulations were carried out on \(L \in \{16,32,64\}\) lattices
        for a subset of the \(\sigma\) and \(T\) used in the previous simulation.
        Also note that the degree \(K\) is
        the same used in \ref{fig:Tc}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
        because it is obviously independent of \(J\).
        Further, note that for small values of \(\sigma\), \(T_c / K\)
        obtained using the fixed coupling strength \(J=1\) coincides with
        \(T_c / \avg{\sum_{\avg{i,j}}J_{ij}}\) obtained using the distance
        dependent coupling strength (see Eq.\ \ref{eq:coupling}).
        This can be expected from the approximate analytic statement presented
        in Sec.\ \ref{sssec:J}.
        \begin{figure}[htb]
            \centering
            \subfigure[][]
            {
                \label{sfig:Tc:RNG_A0}
                \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_A0}
            }
            \subfigure[][]
            {
                \label{sfig:Tc:GG_A0}
                \includegraphics[width=0.45\textwidth]{plots/GG_Tc_A0}
            }
